Learn from ensemble labels

### 2021-03-06 docs/learn_dl_ensemble.Rmd
Some updates and applying OSM to clean labels

---
title: "Run deep learning on AWS instance"
author: "Lei Song"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    highlight: pygments
    toc_depth: 5
---

@@

## Launch instance
The information of instance that we used:

@@

## Parameters setting
After successfully launched the instance, then it is ready to get into the instance to work.

@@

## Experiemnts

### Experiment 1

```
Model: Deeplab3+
train_batch = 32
val_batch = 16
transformation = ['vflip', 'hflip', 'rotate', 'resize']
rotate_degree = [-90, 90]
epoch = 30
lr_init = 0.0005
lr_decay = 0.1
lr_decay_step = 1
momentum = 0.99
criterion = BalancedTverskyFocalLoss(ignore_index=0)
optimizer = "adam"
```

**Result**: terminate early. The model performance stuck quickly. Then it got stuck here.

```
train loss: 0.6423281792689253
train acc: 0.7882347084857799
validation loss: 0.872987336890642
validation acc: 0.8824300759060438
time: 409
[14/100]
train loss: 0.6659585610032082
train acc: 0.7867565039131377
validation loss: 0.8747954650153947
validation acc: 0.8814900846675385
time: 391
```

Seems like BalancedTverskyFocalLoss and adam is a good combination of compiler parameters. The problems left is which model and the learning rate. The experiments shown that the complexity of the model is not enough.

### Experiments

```
Model: Unet

train loss: 0.6717923217349582
train acc: 0.7490688176066788
validation loss: 0.8887722446301649
validation acc: 0.8503072788549024
```

```
Model: Deeper Unet

train loss: 0.6798290364720203
train acc: 0.7305447139121868
validation loss: 0.8891407523390858
validation acc: 0.8469047265690427
time: 245
```

```
Model: VGG 
```

```
Model: ResNet 
```

```
Model: DenseNet 
```

```
Model: SegNet 
```

>>>>

---
title: "Learn from ensemble labels"
author: "Lei Song"
date: "`r Sys.Date()`"
output: 
  rmdformats::readthedown:
    highlight: pygments
    toc_depth: 5
---

@@

## Set up GPU environment
### AWS based method
#### Launch AWS instance
If you decide to use AWS instance, here are some basic steps.
The information of instance that we used:

@@

#### Parameters setting
After successfully launched the instance, then it is ready to get into the instance to work.

@@

### Google Colab
In general, we mean to use Google Colab to run the model. For this case, it is more convenient to read the data locally and pickle them. Then directly load the pickles into Google Colab and just use the GPU environment to run the models.

## Experiemnts
###candidate models

- U-net, which has simple architecture and is friendly to small dataset. This model is especially suitable for guess training.

- Deeplab3plus with ResNet as backbone. This architecture can consider the global context and have skip connections to ensure the complex structure still could get coverage. This model is super useful for the final train with manually corrected labels.

### Label smoothing
The general loss is higher than classic cross entropy loss. But it do help to reduce the gaps between train and validate. So it might be a promising method to use for our case. There is one general parameter "smooth rate". Based on the experiments, a higher smooth rate could help to reduce the gap between train and validate more. 0.5 is a safe choice.
